---
title: "Introduction to Data Science"
subtitle: "Homework 1"
author: "First Name Last name - `flastname@floridapoly.edu`"
output: html_notebook
---



# Problem 1 

During class you completed an activity in which you practiced `git` commands and operations (such as forking a repository, cloning it using `git clone`, and uploading changes using `git push`).

In this exercise you are asked to modify the `flpoly_student.md` file you worked during class, and format it using the **markdown** tools discussed in class. You must **create a table** that shows the courses you are currently enrolled in, using the headers: 

- Prefix: in bold letters (such as **COP**)
- Number: in bold letters (such as **2073**)
- Name: in italics (such as _Introduction to Data Science_)
- Credits (such as 3)

a. Make sure your GitHub repo (`flpoly_DS_2020/`) shows the results of your updated file (remember to use the commands `git add .` , `git commit -m "YOUR MESSAGE"`, and `git push`) 

b. Include a link to your GitHub repo in this document.

~/SP_2020/flpoly_DS_2020 

c. Take a screenshot of the GitHub repo and include it in this document (you can save a copy of the screenshot file in your GitHub repo `flpoly_DS_2020/`)


# Problem 2

For this problem, you are asked to create a list of **3 concepts** you have learned about this semester, for at least 2 of the courses you are currently taking. Include the name of the course as a sub-heading (that is, using `##`), and the concepts as an unordered list. Make sure to include a link to information about the concept you listed.

_Edit this `.Rmd` file to include the solutions here._

## Introduction to Data Science

- Learned how to use several new softwares, and learned what they are used for.
- Learned what GitHub is and how to use it.
- Learned how to make tables in RStudio (this honestly confused me)

## Statistics 1

- Learned the difference between mean, median, and mode
- Learned how to calculate quartiles
- Learned how to properly read charts

# Problem 3

In this problem you will practice some basic R operations. Include solutions to each items by inserting a new R chunk of code (make sure you run the chunk so that the output is displayed)

(a) Create a variable called `my_name` that contains your preferred name.

```{r}
my_name <- "Mike"
```


(b) Create a variable called `name_length` that holds how many letters are in `my_name`.

```{r}
name_length <- nchar(my_name)
```


(c) Show which value is bigger: $e^\pi$ or $\pi^e$. 

```{r}
e <- 2.71828
pi_to_the_e <- pi^e
e_to_the_pi <- e^pi
if(pi_to_the_e > e_to_the_pi){
  print("Pi to the E > E to the Pi")
}else{
  print("Pi to the E < E to the Pi")
}
```


(d) Define a function called `add_tree` that takes a single argument and returns a value 3 times larger than the input.

```{r}
value <- 17
add_tree <- value * 3
print(add_tree)
```


(e) Use the colon operator `:` to create a vector `v` of numbers from 10 to 49. Find the length of this vector using the `length()` function.

```{r}
v <- c(10:49)
length(v)
```


(f) Use the `seq()` function to produce a range of number from -5 to 10 in 0.5 increments.

```{r}
seq(-5, 10, .5)
```


